### 2014-03-17 docs/paper/paper.tex
minor rework of limitations

Both the input and output channels are transport-agnostic and can be attached to application-specific custom hardware that allows for
I/O to be performed over the desired interface, such as Ethernet.

@@

\begin{itemize}
\item encoder instruction buffer size limits number of decoded values that can be encoded

There is an artificial limitation on the complexity of the encoding operation due to the length of the instruction buffer that is used.
With a size of 8192, % FIXME check size
because each encoder must produce 1024 encoded values per timestep, a maximum of eight instructions, and therefore eight decoded values
(not necessarily distinct)
can be used in encoding. It is theoretically possible to implement an encoding operation that requires more decoded values to be used,
but the extra instructions used for this mean that other populations sharing that encoder will have to use fewer.
It is expected that the compiler will be able to detect this scenario and reorganize populations appropriately so as to avoid overfilling the instruction buffers.
\item dimensional restrictions -- 1D, 2D population units
% FIXME citation about why 2D is ``good enough''

As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.
\item four decoded values per population -- using more will create copies of populations to accommodate extra decoders

The choice of using a maximum of four sets of decoder vectors per population is arbitrary; it seems to be a good balance between
population connectivity and memory usage. However, populations that have more than four outgoing connections must be treated specially.
Assuming none of the outgoing connections can be combined together (for example, if the function they decode only differs by a constant),
in order to implement such a population on the simulator, it is necessary to duplicate it and simulate it twice,
once with the first four decoder vectors and again with the remaining ones. The consequence of this is that a population with more than
four outgoing connections will be represented as two or more populations in simulation, thereby reducing the actual number of
distinct populations that can be simulated.
\end{itemize}

@@

% FIXME explanation of the code?
The network was compiled with the Nengo-RT backend to produce a programming file that could be used to configure the simulator hardware.
Simulation output from the FPGA was captured with an Ethernet traffic sniffer and plotted in Figure~\ref{fig:integrator1d}.

>>>>

Both the input and output channels are transport-agnostic and can be attached to application-specific custom hardware that allows for
I/O to be performed over the desired interface, such as Ethernet. The implemented design performs I/O over Gigabit Ethernet using a custom Ethernet frame format for efficiency.

@@

There is an artificial limitation on the complexity of the encoding operation due to the length of the instruction buffer that is used.
Because each encoder must produce 1024 encoded values per timestep, using an instruction memory of size 8192 for each encoder means that a maximum of eight decoded values
can be used as input to each encoder per population.
It is theoretically possible to simulate populations that require more than eight decoded values to be read by a single encoder,
but the extra instructions used for this mean that other populations sharing that encoder will have to use fewer.
It is expected that the compiler will be able to detect this scenario and reorganize populations appropriately so as to avoid overfilling the instruction buffers.

% FIXME citation about why 2D is ``good enough''
As only one-dimensional and two-dimensional population units have been implemented, networks that require populations to compute functions
of three or more independent variables cannot be simulated with this design.

The choice of using a maximum of four sets of decoder vectors per population is arbitrary; it seems to be a good balance between
population connectivity and memory usage. However, populations that have more than four outgoing connections must be treated specially.
Assuming none of the outgoing connections can be combined together (for example, if the function they decode only differs by a constant),
in order to implement such a population on the simulator, it is necessary to duplicate it and simulate it twice,
once with the first four decoder vectors and again with the remaining ones. The consequence of this is that a population with more than
four outgoing connections will be represented as two or more populations in simulation, thereby reducing the actual number of
distinct populations that can be simulated.

@@

% FIXME explanation of the code?
The network was compiled with the \design{} backend to produce a programming file that could be used to configure the simulator hardware.
Simulation output from the FPGA was captured with an Ethernet traffic sniffer and plotted in Figure~\ref{fig:integrator1d}.
